---
params:
  input_la_choice: LA demo
title: "Education, children's social care and offending, descriptive statistics: a focus on `r params$input_la_choice`"
author: "Department for Education"
header-includes:
- \usepackage{longtable}
- \usepackage{graphics}
- \usepackage{xparse}
- \usepackage{moresize}
- \usepackage{setspace}
- \usepackage{tcolorbox}
- \usepackage{wrapfig}
- \usepackage{helvet}
- \usepackage{sectsty}
- \usepackage{fancyhdr}
- \usepackage{xpatch}
- \usepackage{booktabs}
- \usepackage{wrapfig}
- \onehalfspacing
- \pagestyle{fancy}
- \definecolor{gssmidblue}{RGB}{32, 115, 188}
- \definecolor{dfeheadingblue}{RGB}{16, 79, 117}
- \renewcommand{\familydefault}{\sfdefault}
- \allsectionsfont{\color{dfeheadingblue}}
- \sectionfont{\color{dfeheadingblue}\fontsize{16}{18}\selectfont}
- \fancyhead[C]{}
- \fancyhead[L]{\nouppercase{\emph{\leftmark}}}
- \fancyhead[R]{}
- \fancyfoot[R]{\nouppercase{\emph{\rightmark}}}
- \fancyfoot[L]{}
- \renewcommand{\headrulewidth}{0pt}
- \renewcommand{\footrulewidth}{0pt}
- \futurelet\TMPfootrule\def\footrule{{\color{gssmidblue}\TMPfootrule}}
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage[titles]{tocloft}
- \renewcommand{\cftdot}{}
- \AtBeginDocument{\let\maketitle\relax}
- \usepackage{cellspace}
- \usepackage{etoolbox}
- \colorlet{headercolour}{DarkSeaGreen}

output:
  pdf_document:
    df_print: paged
    toc: false
    includes:
      before_body: title.sty
urlcolor: blue
fontsize: 12pt
---

```{r write title page, include=FALSE}
connTitle <- file("title.sty")
writeLines(c(
  "\\resizebox{48mm}{!}{\\includegraphics{www/images/Department_for_Education.png}}\n",
  "\\vspace*{0.24\\textheight}\n",
  "\\Huge{\\color{dfeheadingblue}\\raggedright\\textbf{NEET and participation LA scorecard}} \n",
  paste0("\\huge{\\color{dfeheadingblue}\\textbf{", params$input_la_choice, "}}"),
  "\\vspace*{2\\baselineskip} \n",
  "\\normalsize \n \\newpage \n"
), connTitle)
close(connTitle)
```


```{r load packages, include=FALSE}
knitr::opts_knit$set(root.dir = "./")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
webshot::install_phantomjs()
source("global.R")
source("R/plots.R")
lineLA <- filter(la_ud, la_name == params$input_la_choice)
England <- la_ud %>% filter(geographic_level == "National")

vulnerable_data <- la_ud %>%
  select(
    geographic_level, region_name, la_name,
    NEET_NK_noSEN_percent, NEET_NK_EHCP_percent,
    NEET_NK_SENDsupport_percent, VG_NEET_NK_percentage
  ) %>%
  mutate(
    la_name = case_when(
      geographic_level == "National" ~ "England",
      geographic_level == "Regional" ~ region_name,
      TRUE ~ la_name
    )
  )

vulnerable_data <- vulnerable_data %>%
  mutate(
    NEET_NK_noSEN_percent = as.numeric(NEET_NK_noSEN_percent), NEET_NK_EHCP_percent = as.numeric(NEET_NK_EHCP_percent), NEET_NK_SENDsupport_percent = as.numeric(NEET_NK_SENDsupport_percent),
    VG_NEET_NK_percentage = as.numeric(VG_NEET_NK_percentage)
  )

vulnerable_la <- filter(vulnerable_data, la_name == params$input_la_choice)
vulnerable_england <- vulnerable_data %>% filter(la_name == "England")

participation_data_fte <- la_ud %>%
  select(geographic_level, region_name, la_name, Full_time_education_percent) %>%
  mutate(la_name = case_when(
    geographic_level == "National" ~ "England",
    geographic_level == "Regional" ~ region_name,
    TRUE ~ la_name
  ), participation_type = "Full-time education")

colnames(participation_data_fte)[colnames(participation_data_fte) == "Full_time_education_percent"] <- "value"

participation_data_fte <- participation_data_fte %>%
  select(la_name, participation_type, value)

participation_data_app <- la_ud %>%
  select(geographic_level, region_name, la_name, Apprenticeship_percent) %>%
  mutate(la_name = case_when(
    geographic_level == "National" ~ "England",
    geographic_level == "Regional" ~ region_name,
    TRUE ~ la_name
  ), participation_type = "Apprenticeship")

colnames(participation_data_app)[colnames(participation_data_app) == "Apprenticeship_percent"] <- "value"

participation_data_app <- participation_data_app %>%
  select(la_name, participation_type, value)

participation_data_other <- la_ud %>%
  select(geographic_level, region_name, la_name, Other_education_and_training_percent) %>%
  mutate(la_name = case_when(
    geographic_level == "National" ~ "England",
    geographic_level == "Regional" ~ region_name,
    TRUE ~ la_name
  ), participation_type = "Other")

colnames(participation_data_other)[colnames(participation_data_other) == "Other_education_and_training_percent"] <- "value"

participation_data_other <- participation_data_other %>%
  select(la_name, participation_type, value)

# pull the types together into one file
participation_data <- bind_rows(participation_data_fte, participation_data_app, participation_data_other)

participation_data <- participation_data %>%
  mutate(value = as.numeric(value))

participation_la <- filter(participation_data, la_name == params$input_la_choice)
participation_england <- participation_data %>% filter(la_name == "England")

contextual_data <- la_ud %>%
  select(geographic_level, region_name, la_name, Level_3, L2_em_GCSE_othL2, avg_att8, pt_l2basics_94, sess_overall_percent, sess_overall_percent_pa_10_exact) %>%
  mutate(la_name = case_when(
    geographic_level == "National" ~ "England",
    geographic_level == "Regional" ~ region_name,
    TRUE ~ la_name
  ))


contextual_data <- contextual_data %>%
  select(la_name, Level_3, L2_em_GCSE_othL2, avg_att8, pt_l2basics_94, sess_overall_percent, sess_overall_percent_pa_10_exact)

contextual_data <- contextual_data %>%
  mutate(
    Level_3 = as.numeric(Level_3), L2_em_GCSE_othL2 = as.numeric(L2_em_GCSE_othL2), avg_att8 = as.numeric(avg_att8),
    pt_l2basics_94 = as.numeric(pt_l2basics_94), sess_overall_percent = as.numeric(sess_overall_percent), sess_overall_percent_pa_10_exact = as.numeric(sess_overall_percent_pa_10_exact)
  )

contextual_la <- filter(contextual_data, la_name == params$input_la_choice)
contextual_england <- contextual_data %>% filter(la_name == "England")
```

# NEET and not known

```{r gauge_chart_neetnk, echo=FALSE, out.width="200%"}
plot_neetnkgauge(la_ud, lineLA, England,title=TRUE) %>%
  layout(autosize = F, width = 960, height = 320)
```

\vspace{-5.8cm}

```{r derive_neetnk_vbox_values, echo=FALSE}
NEET_nk_perc <- lineLA %>%
  pull(as.numeric(NEET_not_known_percent))

NEET_nk_change <- lineLA %>%
  pull(as.numeric(annual_change_ppts_NEET_not_known))

NEET_nk_perc_Eng <- England %>%
  pull(as.numeric(NEET_not_known_percent))

NEET_nk_change_Eng <- England %>%
  pull(as.numeric(annual_change_ppts_NEET_not_known))

Regionname <- lineLA %>%
  pull(region_name)

NEET_nk_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(NEET_not_known_percent))

NEET_nk_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(annual_change_ppts_NEET_not_known))
```

\begin{center}
\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.75\linewidth,
 boxrule=0pt,
 equal height group=introbox
 ]
`r paste0(NEET_nk_perc, "\\%, ", change_ed(NEET_nk_change), NEET_nk_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", NEET_nk_perc_region, "\\%, ", change_ed(NEET_nk_change_region), NEET_nk_change_region, " ppts.")`

`r paste0("England: ", NEET_nk_perc_Eng, "\\%, ", change_ed(NEET_nk_change_Eng), NEET_nk_change_Eng, " ppts.")`

`r paste0("Annual changes are since end ", previous_year_end, ".")`
\end{tcolorbox}
\end{center}


```{r gauge_chart_neet, echo=FALSE, out.width="200%"}
fig <- plot_neetgauge(la_ud, lineLA, England, xdomain = c(0.04, 0.46),title=TRUE)
plot_nkgauge(la_ud, lineLA, England, fig = fig, xdomain = c(0.54, 0.96),title=TRUE) %>%
  layout(autosize = T, width = 960, height = 240)
```

\vspace{-5.8cm}

```{r derive_neet_vbox_values, echo=FALSE}
NEET_perc <- lineLA %>%
  pull(as.numeric(NEET_percent))

NEET_change <- lineLA %>%
  pull(as.numeric(annualchange_NEET))

NEET_perc_Eng <- England %>%
  pull(as.numeric(NEET_percent))

NEET_change_Eng <- England %>%
  pull(as.numeric(annualchange_NEET))

Regionname <- lineLA %>%
  pull(region_name)

NEET_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(NEET_percent))

NEET_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(annualchange_NEET))
```

```{r derive_nk_vbox_values, echo=FALSE}
Nk_perc <- lineLA %>%
  pull(as.numeric(Notknown_percent))

Nk_change <- lineLA %>%
  pull(as.numeric(annualchange_notknown))

Nk_perc_Eng <- England %>%
  pull(as.numeric(Notknown_percent))

Nk_change_Eng <- England %>%
  pull(as.numeric(annualchange_notknown))

Regionname <- lineLA %>%
  pull(region_name)

Nk_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(Notknown_percent))

Nk_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(annualchange_notknown))
```

\makebox[1.00\linewidth]{
\centering

\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.49\linewidth,
 boxrule=0pt,
 equal height group=neetbox
 ]
`r paste0(NEET_perc, "\\%, ", change_ed(NEET_change), NEET_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", NEET_perc_region, "\\%, ", change_ed(NEET_change_region), NEET_change_region, " ppts.")`

`r paste0("England: ", NEET_perc_Eng, "\\%, ", change_ed(NEET_change_Eng), NEET_change_Eng, " ppts.")`

`r paste0("Annual changes are since end ", previous_year_end, ".")`
\end{tcolorbox}


\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.49\linewidth,
 boxrule=0pt,
 equal height group=neetbox
 ]
`r paste0(Nk_perc, "\\%, ", change_ed(Nk_change), Nk_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", Nk_perc_region, "\\%, ", change_ed(Nk_change_region), Nk_change_region, " ppts.")`

`r paste0("England: ", Nk_perc_Eng, "\\%, ", change_ed(Nk_change_Eng), Nk_change_Eng, " ppts.")`

`r paste0("Annual changes are since end ", previous_year_end, ".")`
\end{tcolorbox}
}

\newpage

# Vulnerable Groups NEET

\begin{wrapfigure}{l}{0.56\textwidth}
```{r bar_chart_vuln, echo=FALSE, out.width="105%"}
plot_vulnerablebar(vulnerable_data, vulnerable_la, lineLA, vulnerable_england,
  plotcat = "VG_NEET_NK_percentage"
)
```
\end{wrapfigure}

A young person is said to be in a vulnerable group if they have any of the following characteristics (taken from IC01 of the NCCIS returns):     
110 - Looked after/In care  
130 - Refugee/Asylum seeker  
140 - Carer-not own child  
150 - Disclosed substance misuse   
160 - Care leaver   
170 - Supervised by YOT  
190 - Parent-not caring for own child  
200 - Alternative provision  
210 - Mental health flag  

---

```{r bar_chart_vuln2, echo=FALSE, out.hold=TRUE, out.width="35%"}
plot_vulnerablebar(vulnerable_data, vulnerable_la, lineLA, vulnerable_england,
  plotcat = "NEET_NK_noSEN_percent"
)
plot_vulnerablebar(vulnerable_data, vulnerable_la, lineLA, vulnerable_england,
  plotcat = "NEET_NK_EHCP_percent"
)
plot_vulnerablebar(vulnerable_data, vulnerable_la, lineLA, vulnerable_england,
  plotcat = "NEET_NK_SENDsupport_percent"
)
```

\newpage

# Participation
## Participating in education and training

```{r part_guage, echo=FALSE, out.width="200%"}
plot_partgauge(la_ud, lineLA, England) %>%
  layout(autosize = F, width = 960, height = 360)
```

\vspace{-5.8cm}

```{r derive_part_vbox_values, echo=FALSE}
participating_perc <- lineLA %>%
  pull(as.numeric(TOTAL_participating_in_education_and_training_percent))

participating_change <- lineLA %>%
  pull(as.numeric(annual_change_Participation_in_education_training))

participating_perc_Eng <- England %>%
  pull(as.numeric(TOTAL_participating_in_education_and_training_percent))

participating_change_Eng <- England %>%
  pull(as.numeric(annual_change_Participation_in_education_training))

Regionname <- lineLA %>%
  pull(region_name)

participating_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(TOTAL_participating_in_education_and_training_percent))

participating_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(annual_change_Participation_in_education_training))
```

\begin{center}
\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.75\linewidth,
 boxrule=0pt,
 equal height group=introbox
 ]
`r paste0(participating_perc, "\\%, ", change_ed(participating_change), participating_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", participating_perc_region, "\\%, ", change_ed(participating_change_region), participating_change_region, " ppts.")`

`r paste0("England: ", participating_perc_Eng, "\\%, ", change_ed(participating_change_Eng), participating_change_Eng, " ppts.")`

`r paste0("Annual changes are since March ", last_year, ".")`
\end{tcolorbox}
\end{center}

### Type of education and training
```{r part_bar, echo=FALSE, out.width="50%"}
plot_participationbar(participation_data, participation_la, lineLA, participation_england)
```


## September Guarantee: % offered an education place

```{r gauge_chart_Sept_Guar, echo=FALSE, out.width="200%"}
Sept_Guar_gauge(la_ud, lineLA, England) %>%
  layout(autosize = F, width = 960, height = 320)
```

\vspace{-5.8cm}

```{r derive_septguar_vbox_values, echo=FALSE}
Sept_Guar_perc <- lineLA %>%
  pull(as.numeric(September_guarantee_Offer_made_percent))

Sept_Guar_change <- lineLA %>%
  pull(as.numeric(September_guarantee_annual_change_ppts))

Sept_Guar_perc_Eng <- England %>%
  pull(as.numeric(September_guarantee_Offer_made_percent))

Sept_Guar_change_Eng <- England %>%
  pull(as.numeric(September_guarantee_annual_change_ppts))

Regionname <- lineLA %>%
  pull(region_name)

Sept_Guar_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(September_guarantee_Offer_made_percent))

Sept_Guar_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
  pull(as.numeric(September_guarantee_annual_change_ppts))
```

\begin{center}
\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.75\linewidth,
 boxrule=0pt,
 equal height group=introbox
 ]
`r paste0(Sept_Guar_perc, "\\%, ", change_ed(Sept_Guar_change), Sept_Guar_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", Sept_Guar_perc_region, "\\%, ", change_ed(Sept_Guar_change_region), Sept_Guar_change_region, " ppts.")`

`r paste0("England: ", Sept_Guar_perc_Eng, "\\%, ", change_ed(Sept_Guar_change_Eng), Sept_Guar_change_Eng, " ppts.")`

`r paste0("Annual changes are since September ", previous_year_end, ".")`
\end{tcolorbox}
\end{center}

\newpage

# Contextual - attainment and attendance
### Post 16 attainment

```{r bar_chart_contextual1, echo=FALSE, out.hold=TRUE, out.width="50%"}
plot_contextualbar(contextual_data, contextual_la, lineLA, contextual_england,
  plotcat = "Level_3"
)
plot_contextualbar(contextual_data, contextual_la, lineLA, contextual_england,
  plotcat = "L2_em_GCSE_othL2"
)
```

### GCSE attainment
```{r bar_chart_contextual2, echo=FALSE, out.hold=TRUE, out.width="50%"}
plot_contextualbar(contextual_data, contextual_la, lineLA, contextual_england,
  plotcat = "avg_att8"
)
plot_contextualbar(contextual_data, contextual_la, lineLA, contextual_england,
  plotcat = "pt_l2basics_94"
)
```

### School attendance
```{r bar_chart_contextual3, echo=FALSE, out.hold=TRUE, out.width="50%"}
plot_contextualbar(contextual_data, contextual_la, lineLA, contextual_england,
  plotcat = "sess_overall_percent"
)
plot_contextualbar(contextual_data, contextual_la, lineLA, contextual_england,
  plotcat = "sess_overall_percent_pa_10_exact"
)
```

### 16-17 LA population
```{r derive_pop_ons_vbox_values, echo=FALSE}
ONS_population <- lineLA %>%
  pull(Age1617_ONS_population) %>%
  as.numeric()
```

```{r derive_pop_nccis_vbox_values, echo=FALSE}
NCCIS_population <- lineLA %>%
  pull(Cohort_DJFavg) %>%
  as.numeric()
```

\makebox[1.00\linewidth]{
\centering

\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.49\linewidth,
 boxrule=0pt,
 equal height group=popbox
 ]
`r format(ONS_population, big.mark = ",")`
\tcblower
`r paste0("ONS estimate")`
\end{tcolorbox}


\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.49\linewidth,
 boxrule=0pt,
 equal height group=popbox
 ]
`r format(NCCIS_population, big.mark = ",")`
\tcblower
`r paste0("Recorded on CCIS")`
\end{tcolorbox}
}
