---
params:
  input_la_choice: LA demo
title: "Education, children's social care and offending, descriptive statistics: a focus on `r params$input_la_choice`"
author: "Department for Education"
header-includes:
- \usepackage{longtable}
- \usepackage{graphics}
- \usepackage{xparse}
- \usepackage{moresize}
- \usepackage{setspace}
- \usepackage{tcolorbox}
- \usepackage{wrapfig}
- \usepackage{helvet}
- \usepackage{sectsty}
- \usepackage{fancyhdr}
- \usepackage{xpatch}
- \usepackage{booktabs}
- \usepackage{wrapfig}
- \onehalfspacing
- \pagestyle{fancy}
- \definecolor{gssmidblue}{RGB}{32, 115, 188}
- \definecolor{dfeheadingblue}{RGB}{16, 79, 117}
- \renewcommand{\familydefault}{\sfdefault}
- \allsectionsfont{\color{dfeheadingblue}}
- \sectionfont{\color{dfeheadingblue}\fontsize{16}{18}\selectfont}
- \fancyhead[C]{}
- \fancyhead[L]{\nouppercase{\emph{\leftmark}}}
- \fancyhead[R]{}
- \fancyfoot[R]{\nouppercase{\emph{\rightmark}}}
- \fancyfoot[L]{}
- \renewcommand{\headrulewidth}{0pt}
- \renewcommand{\footrulewidth}{0pt}
- \futurelet\TMPfootrule\def\footrule{{\color{gssmidblue}\TMPfootrule}}
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage[titles]{tocloft}
- \renewcommand{\cftdot}{}
- \AtBeginDocument{\let\maketitle\relax}
- \usepackage{cellspace}
- \usepackage{etoolbox}
- \colorlet{headercolour}{DarkSeaGreen}

output:
  pdf_document:
    df_print: paged
    toc: false
    includes:
      before_body: title.sty
urlcolor: blue
fontsize: 12pt
---

```{r write title page, include=FALSE}
connTitle <- file("title.sty")
writeLines(c("\\resizebox{48mm}{!}{\\includegraphics{www/images/Department_for_Education.png}}\n",
             "\\vspace*{0.24\\textheight}\n",
             "\\Huge{\\color{dfeheadingblue}\\raggedright\\textbf{NEET and participation LA scorecard}} \n", 
             paste0("\\huge{\\color{dfeheadingblue}\\textbf{",params$input_la_choice,"}}"),
             "\\vspace*{2\\baselineskip} \n",
             "\\normalsize \n \\newpage \n"), connTitle)
close(connTitle)
```


```{r load packages, include=FALSE}
knitr::opts_knit$set(root.dir = './')
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
webshot::install_phantomjs()
source('global.R')
source('R/plots.R')
lineLA  <- filter(la_ud, la_name == params$input_la_choice)
England <- la_ud %>% filter(geographic_level == "National")

vulnerable_data <- la_ud %>% 
  select(geographic_level, region_name, la_name,
         NEET_NK_noSEN_percent, NEET_NK_EHCP_percent, 
         NEET_NK_SENDsupport_percent, VG_NEET_NK_percentage) %>%
    mutate(
      la_name = case_when(
      geographic_level == "National" ~ "England",
      geographic_level == "Regional" ~ region_name,
      TRUE ~ la_name
    )
    )
vulnerable_la      <- filter(vulnerable_data, la_name == params$input_la_choice)
vulnerable_england <- vulnerable_data %>% filter(la_name == "England")

```

# NEET and not known

```{r gauge_chart_neetnk, echo=FALSE, out.width="200%"}
plot_neetnkgauge(la_ud, lineLA, England) %>% 
  layout(autosize = F, width = 960, height = 320)
```

\vspace{-5.8cm}

```{r derive_neetnk_vbox_values, echo=FALSE}
    NEET_nk_perc <- lineLA %>%
      pull(as.numeric(NEET_not_known_percent))

    NEET_nk_change <- lineLA %>%
      pull(as.numeric(annual_change_ppts_NEET_not_known))

    NEET_nk_perc_Eng <- England %>%
      pull(as.numeric(NEET_not_known_percent))

    NEET_nk_change_Eng <- England %>%
      pull(as.numeric(annual_change_ppts_NEET_not_known))

    Regionname <- lineLA %>%
      pull(region_name)

    NEET_nk_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
      pull(as.numeric(NEET_not_known_percent))

    NEET_nk_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
      pull(as.numeric(annual_change_ppts_NEET_not_known))
```


\begin{center}
\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.49\linewidth,
 boxrule=0pt,
 equal height group=introbox
 ]
`r paste0(NEET_nk_perc, "\\%, ", change_ed(NEET_nk_change), NEET_nk_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", NEET_nk_perc_region, "\\%, ", change_ed(NEET_nk_change_region), NEET_nk_change_region, " ppts.")`

`r paste0("England: ", NEET_nk_perc_Eng, "\\%, ", change_ed(NEET_nk_change_Eng), NEET_nk_change_Eng, " ppts.")`

`r paste0("Annual changes are since end ", previous_year_end, ".")`
\end{tcolorbox}
\end{center}


```{r gauge_chart_neet, echo=FALSE, out.width="200%"}
fig <- plot_neetgauge(la_ud, lineLA, England, xdomain=c(0.04,0.46))
plot_nkgauge(la_ud, lineLA, England, fig=fig, xdomain=c(0.54,0.96)) %>% 
  layout(autosize = T, width = 960, height = 240)
```

\vspace{-5.8cm}

```{r derive_neet_vbox_values, echo=FALSE}
    NEET_perc <- lineLA %>%
      pull(as.numeric(NEET_percent))

    NEET_change <- lineLA %>%
      pull(as.numeric(annualchange_NEET))

    NEET_perc_Eng <- England %>%
      pull(as.numeric(NEET_percent))

    NEET_change_Eng <- England %>%
      pull(as.numeric(annualchange_NEET))

    Regionname <- lineLA %>%
      pull(region_name)

    NEET_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
      pull(as.numeric(NEET_percent))

    NEET_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
      pull(as.numeric(annualchange_NEET))
```

```{r derive_nk_vbox_values, echo=FALSE}
    Nk_perc <- lineLA %>%
      pull(as.numeric(Notknown_percent))

    Nk_change <- lineLA %>%
      pull(as.numeric(annualchange_notknown))

    Nk_perc_Eng <- England %>%
      pull(as.numeric(Notknown_percent))

    Nk_change_Eng <- England %>%
      pull(as.numeric(annualchange_notknown))

    Regionname <- lineLA %>%
      pull(region_name)

    Nk_perc_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
      pull(as.numeric(Notknown_percent))

    Nk_change_region <- filter(la_ud, geographic_level == "Regional", region_name == Regionname) %>%
      pull(as.numeric(annualchange_notknown))
```

\makebox[1.00\linewidth]{
\centering

\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.49\linewidth,
 boxrule=0pt,
 equal height group=introbox
 ]
`r paste0(NEET_perc, "\\%, ", change_ed(NEET_change), NEET_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", NEET_perc_region, "\\%, ", change_ed(NEET_change_region), NEET_change_region, " ppts.")`

`r paste0("England: ", NEET_perc_Eng, "\\%, ", change_ed(NEET_change_Eng), NEET_change_Eng, " ppts.")`

`r paste0("Annual changes are since end ", previous_year_end, ".")`
\end{tcolorbox}


\begin{tcolorbox}[colback=gssmidblue, 
 leftright skip=0.1cm,
 coltext=white, 
 halign=left, 
 fontupper={\Large \bfseries},
 fontlower={\normalsize \bfseries},
 sharp corners, 
 colframe=gssmidblue,
 width=0.49\linewidth,
 boxrule=0pt,
 equal height group=introbox
 ]
`r paste0(Nk_perc, "\\%, ", change_ed(Nk_change), Nk_change, " ppts")`
\tcblower
`r paste0(Regionname, ": ", Nk_perc_region, "\\%, ", change_ed(Nk_change_region), Nk_change_region, " ppts.")`

`r paste0("England: ", Nk_perc_Eng, "\\%, ", change_ed(Nk_change_Eng), Nk_change_Eng, " ppts.")`

`r paste0("Annual changes are since end ", previous_year_end, ".")`
\end{tcolorbox}
}

\newpage

# Vulnerable Groups NEET

\begin{wrapfigure}{l}{0.56\textwidth}
```{r bar_chart_vuln, echo=FALSE, out.width="110%"}
plot_vulnerablebar(vulnerable_data, vulnerable_la,  lineLA, vulnerable_england, 
                               plotcat='VG_NEET_NK_percentage')
```
\end{wrapfigure}

A young person is said to be in a vulnerable group if they have any of the following characteristics (taken from IC01 of the NCCIS returns):     
110 - Looked after/In care  
130 - Refugee/Asylum seeker  
140 - Carer-not own child  
150 - Disclosed substance misuse   
160 - Care leaver   
170 - Supervised by YOT  
190 - Parent-not caring for own child  
200 - Alternative provision  
210 - Mental health flag  

---

```{r bar_chart_vuln2, echo=FALSE, out.hold=TRUE, out.width="32%"}
plot_vulnerablebar(vulnerable_data, vulnerable_la,  lineLA, vulnerable_england, 
                               plotcat='NEET_NK_EHCP_percent')
plot_vulnerablebar(vulnerable_data, vulnerable_la,  lineLA, vulnerable_england, 
                               plotcat='NEET_NK_SENDsupport_percent')
plot_vulnerablebar(vulnerable_data, vulnerable_la,  lineLA, vulnerable_england, 
                               plotcat='NEET_NK_noSEN_percent')
```


# Participation

# Contextual - attainment and attendance



